---
title: "Telecom Customer Churn Prediction"
author: "Xiaoying Yang, Bo Yang, Yin Tip Ho"
date: "4/28/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval=FALSE)
```

## Problem Statement
Customer churn calculates the percentage of customers who stopped using your company's product or service during a certain time frame. 

#### Key Takeaways
* Customer churn analysis helps businesses understand why customers don’t return for repeat business.
* Churn rate tells you what portion of your customers leave over a period of time.
* It’s often useful to look at churn by product, region or other granular factors.
* Businesses with ERP systems may be able to generate customer churn analysis reports using pre-built dashboards and automated reporting tools. Others will need to do some manual number crunching.


## Target

* Identify if the churn variables on characteristics of customers to determine if they will keep using the products and services by classification on their associations;
* Predict which characteristics of customers are most likely to lose and put forward suggestions for retaining users to the maximum extent according to the properties of losing customers.


## Data Description

This data set consists of 100 variables and approximately 100 thousand records. 
This data set contains different variables explaining the attributes of telecom industry and various factors considered important while dealing with customers of telecom industry. 
The target variable here is churn which explains whether the customer will churn or not.

#### Customer Usage Behavior  

* Price 
* Calling 
* Flow
* Time 

#### Customer Atributes

* Interaction with Telecom Operators
* Family
* Social Relations
* Financial Assets
* Facilities
* Others

#### Variable Description
1 rev_Mean: Mean monthly revenue (charge amount)
2 mou_Mean: Mean number of monthly minutes of use
3 totmrc_Mean: Mean total monthly recurring charge
4 da_Mean: Mean number of directory assisted calls
5 ovrmou_Mean: Mean overage minutes of use
6 ovrrev_Mean: Mean overage revenue
7 vceovr_Mean: Mean revenue of voice overage
8 datovr_Mean: Mean revenue of data overage
9 roam_Mean: Mean number of roaming calls
10 change_mou: Percentage change in monthly minutes of use vs previous three month average
11 change_rev: Percentage change in monthly revenue vs previous three month average
12 drop_vce_Mean: Mean number of dropped (failed) voice calls
13 drop_dat_Mean: Mean number of dropped (failed) data calls
14 blck_vce_Mean: Mean number of blocked (failed) voice calls
15 blck_dat_Mean: Mean number of blocked (failed) data calls
16 unan_vce_Mean: Mean number of unanswered voice calls
17 unan_dat_Mean: Mean number of unanswered data calls
18 plcd_vce_Mean: Mean number of attempted voice calls placed
19 plcd_dat_Mean: Mean number of attempted data calls placed
20 recv_vce_Mean: Mean number of received voice calls
21 recv_sms_Mean: N
22 comp_vce_Mean: Mean number of completed voice calls
23 comp_dat_Mean: Mean number of completed data calls
24 custcare_Mean: Mean number of customer care calls
25 ccrndmou_Mean: Mean rounded minutes of use of customer care calls
26 cc_mou_Mean: Mean unrounded minutes of use of customer care (see CUSTCARE_MEAN) calls
27 inonemin_Mean: Mean number of inbound calls less than one minute
28 threeway_Mean: Mean number of three way calls
29 mou_cvce_Mean: Mean unrounded minutes of use of completed voice calls
30 mou_cdat_Mean: Mean unrounded minutes of use of completed data calls
31 mou_rvce_Mean: Mean unrounded minutes of use of received voice calls
32 owylis_vce_Mean: Mean number of outbound wireless to wireless voice calls
33 mouowylisv_Mean: Mean unrounded minutes of use of outbound wireless to wireless voice calls
34 iwylis_vce_Mean: N
35 mouiwylisv_Mean: Mean unrounded minutes of use of inbound wireless to wireless voice calls
36 peak_vce_Mean: Mean number of inbound and outbound peak voice calls
37 peak_dat_Mean: Mean number of peak data calls
38 mou_peav_Mean: Mean unrounded minutes of use of peak voice calls
39 mou_pead_Mean: Mean unrounded minutes of use of peak data calls
40 opk_vce_Mean: Mean number of off-peak voice calls
41 opk_dat_Mean: Mean number of off-peak data calls
42 mou_opkv_Mean: Mean unrounded minutes of use of off-peak voice calls
43 mou_opkd_Mean: Mean unrounded minutes of use of off-peak data calls
44 drop_blk_Mean: Mean number of dropped or blocked calls
45 attempt_Mean: Mean number of attempted calls
46 complete_Mean: Mean number of completed calls
47 callfwdv_Mean: Mean number of call forwarding calls
48 callwait_Mean: Mean number of call waiting calls
49 churn: Instance of churn between 31-60 days after observation date
50 months: Total number of months in service
51 uniqsubs: Number of unique subscribers in the household
52 actvsubs: Number of active subscribers in household
53 new_cell: New cell phone user
54 crclscod: Credit class code
55 asl_flag: Account spending limit
56 totcalls: Total number of calls over the life of the customer
57 totmou: Total minutes of use over the life of the cus
58 totrev: Total revenue
59 adjrev: Billing adjusted total revenue over the life of the customer
60 adjmou: Billing adjusted total minutes of use over the life of the customer
61 adjqty: Billing adjusted total number of calls over the life of the customer
62 avgrev: Average monthly revenue over the life of the customer
63 avgmou: Average monthly minutes of use over the life of the customer
64 avgqty: Average monthly number of calls over the life of the customer
65 avg3mou: Average monthly minutes of use over the previous three months
66 avg3qty: Average monthly number of calls over the previous three months
67 avg3rev: Average monthly revenue over the previous three months
68 avg6mou: Average monthly minutes of use over the previous six months
69 avg6qty: Average monthly number of calls over the previous six months
70 avg6rev: Average monthly revenue over the previous six months
71 prizm_social_one: Social group letter only
72 area: Geogrpahic area
73 dualband: Dualband
74 refurb_new: Handset: refurbished or new
75 hnd_price: Current handset price
76 phones: Number of handsets issued
77 models: Number of models issued
78 hnd_webcap: Handset web capability
79 truck: Truck indicator
80 rv: RV indicator
81 ownrent: Home owner/renter status
82 lor: Length of residence
83 dwlltype: Dwelling Unit type
84 marital: Marital Status
85 adults: Number of adults in household
86 infobase: InfoBase match
87 income: Estimated income
88 numbcars: Known number of vehicles
89 HHstatin: Premier household status indicator
90 dwllsize: Dwelling size
91 forgntvl: Foreign travel dummy variable
92 ethnic: Ethnicity roll-up code
93 kid0_2: Child 0 - 2 years of age in household
94 kid3_5: Child 3 - 5 years of age in household
95 kid6_10: Child 6 - 10 years of age in household
96 kid11_15: Child 11 - 15 years of age in household
97 kid16_17: Child 16 - 17 years of age in household
98 creditcd: Credit card indicator
99 eqpdays: Number of days (age) of current equipment
100 Customer_ID: N

## Project Guide 

* Data Wrangling
    + Missing Values 
* Feature Engineering
    + check correlation
    + scaling 
* Principle Component Analysis
* Factor Analysis and Clustering
    + numerical feature selection
    + factor analysis
* Clustering
    + K-Means
    + Mahalanobis distance K-Means
    + Kernel K-Means
    + Hierarchical Clustering
    + EM Clustering
* Prediction Models
    + Subset for better modelling
    + Logistic Regression
    + KNN
    + Decision Tree
    + Random Forest


## References
https://www.kaggle.com/datasets/abhinav89/telecom-customer

## CODE
#### Data Wrangling

* Import Data and load library

```{r Import Data and load library}
    library(tidyverse)
    library(zoo)
    library(gtools)
    library(naniar)
    library(mice)
    library(ggcorrplot)
    library(rlang)
    library(factoextra)
    library(kernlab)
    library(glmnet)
    library(fastDummies)
    library(caret)
    library(class)
    library(e1071)
    library(randomForest)
    library(glmnet)
    library(partykit)
    raw_data <- read_csv("Telecom_customer churn.csv")

```

* Missing Values

```{r Check missing values}
#check missing values by columns
raw_data %>% miss_var_summary()

#Remove the columns with more than 10% missing values 
telecom <- raw_data %>%
    select(-c(numbcars, HHstatin, dwllsize, ownrent, dwlltype, lor,income, 
              adults, infobase, hnd_webcap)) %>%
    select(-prizm_social_one)  #remove unrelated col with high missing rate

telecom1 <- telecom
var_miss <- which(colMeans(is.na(telecom1))!= 0)
var_miss
# 33 variables still have missing value.

# Numeric type var
nr_mice <- select_if(telecom1, negate(is.numeric))
r_mice <- select_if(telecom1, is.numeric)
na_mice <- r_mice[, c(69, 70, 74)]
r_mice <- r_mice[, -c(69, 70, 74)]

# Imputation by rf
impute <- mice(r_mice, method = "rf", ntree = 50, m = 1, maxit = 1)
telecom_complete <- complete(impute)
any(is.na(telecom_complete))
# Add non-numeric type var back to the data set
telecom1 <- cbind(telecom_complete, na_mice, nr_mice)
sum(is.na(telecom1))
var_miss1 <- which(colMeans(is.na(telecom1))!= 0)
var_miss1
# Row missing value
row_miss <- which(rowMeans(is.na(telecom1)) != 0)
length(row_miss)

telecom1 <- telecom1[-row_miss, ]

save(telecom1, file = "telecom_Comsumer_Info.RData")
```

```{r frequency table}
table(telecom1$churn)
#0.5
```


#### Feature Engineering

Transform some numeric variables into factors because they are only 0 or 1.
Create a separate data set without the churn variable (variable to predict) that will be the one we work on.
Enumerate the rows of the data set with the Customers ID so we can identify each.
Remove unnecessary variables with a correlation matrix, and remove some that are also not important.

```{r Check correlations}
# Function to transform variables
REMOVE = "remove"
TO_FACTOR = "tofactor"

editCol <- function(colNames, df, todo) {
  for(col in colNames) {
    index <- which(names(df) == col)
    if(!is_empty(index)) {
      if(todo == REMOVE) {
        df <- df[, -index]
      } else if(todo == TO_FACTOR) {
        df[, index]  <- as.factor(df[, index])
      } else {errorCondition("Not performing well")}
    }
  }
  return(df)
}

# Perform the function
telecom1 <- editCol(c("forgntv1", "truck", "rv"), telecom1, TO_FACTOR)
telecom1 <- droplevels.data.frame(telecom1)
row.names(telecom1) <- telecom1$Customer_ID
telecom_customer <- telecom1
telecom1 <- editCol(c("churn", "Customer_ID"), telecom1, REMOVE)

rm(list = setdiff(ls(), c("telecom1", "telecom_customer")))

# Correlation matrix
r_mice <- select_if(telecom1, is.numeric)
Corr <- cor(r_mice)
#Corr[upper.tri(Corr)] = 0

ggcorrplot(corr = Corr, type = "lower",tl.srt = 90, tl.cex = 8)


# devtools::install_github("laresbernardo/lares")
library(lares)

corr_cross(r_mice, # name of dataset
  max_pvalue = 0.05, # display only significant correlations (at 5% level)
  top = 10 # display top 10 couples of variables (by correlation coefficient)
)


col <- colorRampPalette(c("darkblue", "white", "darkorange"))(20)
M <- cor(r_mice)
heatmap(x = M, col = col, symm = TRUE)








  # Need to eliminate strong correlated variables
diag(Corr) = 0
 
telecom_num_no_corr <-  r_mice[, !apply(Corr, 2, function(x) any(abs(x) > 0.9, na.rm = TRUE))]
# How many variables are eliminated
dim(r_mice)[2] - dim(telecom_num_no_corr)[2]
```
```{r heat map}
corr_mat = round(cor(r_mice),2)

corr_mat[lower.tri(corr_mat)] <- NA
 
melted_corr_mat <- melt(corr_mat)

ggplot(data = melted_corr_mat, aes(Var2, Var1, fill = value))+
 geom_tile(color = "white")+
 scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
  theme_minimal()+ 
 theme(axis.text.x = element_text(angle = 90, vjust = 1, 
    size = 3, hjust = 1),
    axis.text.y = element_text(size = 3))+
 coord_fixed()
```

* Scaling
```{r Scaling}
 #hist
    par(mfrow = c(3,4))
    for (i in 1:ncol(telecom_num_no_corr)){
        hist(telecom_num_no_corr[,i],
             breaks = 30,
             main = "",ylab = "",
             xlab = names(telecom_num_no_corr)[i],
             cex.axis=0.5,
             cex.lab = 0.6)
    }
    
    #scaling and his again
    telecom_num_scale = as.data.frame(scale(telecom_num_no_corr))
     par(mfrow = c(3,4))
    for (i in 1:ncol(telecom_num_scale)){
        hist(telecom_num_scale[,i],
             breaks = 30,
             main = "",ylab = "",
             xlab = names(telecom_num_no_corr)[i],
             cex.axis=0.5,
             cex.lab = 0.6)
    }

    save(telecom_num_scale, file = "telecom_num_scale.RData")
```


#### PCA
Principle Components Analysis

```{r pca}
pca_tele <- prcomp(telecom_num_scale)
# pca_tele #发现太长了就用summary
summary(pca_tele)
var_expalained <- pca_tele$sdev^2/sum(pca_tele$sdev^2)

# Scree plot
fviz_screeplot(pca_tele, addlabels = TRUE) # Scree plot
qplot(c(1:49), var_expalained) + geom_line() + xlab("Principal Component") + ylab("Variance Explained") + ggtitle("Scree Plot") + ylim(0, 1)
print(var_expalained)

# Visualize contributions of pca in different dimensions
fviz_contrib(pca_tele,choice = "var", axes = 1)
fviz_contrib(pca_tele,choice = "var", axes = 2)
fviz_contrib(pca_tele,choice = "var", axes = 3)

# MCA for individual
fviz_contrib(pca_tele, choice = "ind", axes = 2, top = 100)# Difference between customers

# PCA RADOR PLOT
fviz_pca_var(pca_tele, col.var = "contrib")

# PCA biplot
fviz_pca_biplot(pca_tele, repel = TRUE)

# Customers on 1st and 2nd components
fviz_pca_ind(pca_tele,
             label = "none", # hide individual labels
             habillage = telecom_complete$churn, # color by groups
             palette = c("#00AFBB", "#E7B800"))
#ggg
#testing function:  pls no error
```

#### Factor Analysis

```{r select important numerical variables}
colsImportant = c()

colsImportant = c(colsImportant, 
                  names(sort(pca_tele$rotation[, 1], decreasing = TRUE)[1:21]))
colsImportant = c(colsImportant, 
                  names(sort(pca_tele$rotation[, 2], decreasing = TRUE)[1:8]))
colsImportant = c(colsImportant, 
                  names(sort(pca_tele$rotation[, 3], decreasing = TRUE)[1:5]))

colsImportant = unique(colsImportant)
```
```
As the variables are too big for the factor analysis, we will reduce it. 
We use PCA with the most important variables of the PCs to reduce it. 
We use the ones that are high enough, given by the graphs above.
```
```{r factor analysis}
#remove the not so important variables and then do factor analysis
tele_num_scale_imp = telecom_num_scale %>%
    select(c(colsImportant))
save(tele_num_scale_imp, file = "tele_num_scale_imp.RData")


x.f = factanal(tele_num_scale_imp, factors = 5,
               rotation="none", scores="regression")

factor = cbind(x.f$loadings, x.f$uniquenesses)
#factor

#graph each factor 
par(mfrow=c(3,1))
barplot(x.f$loadings[,1], names=F, las=2, col="darkblue", ylim = c(-1, 1))
barplot(x.f$loadings[,2], names=F, las=2, col="darkblue", ylim = c(-1, 1))
barplot(x.f$loadings[,3], names=F, las=2, col="darkblue", ylim = c(-1, 1))
barplot(x.f$loadings[,4], names=F, las=2, col="darkblue", ylim = c(-1, 1))
barplot(x.f$loadings[,5], las=2, col="darkblue", ylim = c(-1, 1))

```
```
In the graph, at first sight we can discard the 4, 5 factors as they are not pretty
much meaningful in any manner. 
Also the factor 3 does not look like anything that important.

However, factors 1 and 2 show really interesting inverse correlations. 
They differ on the exact variables and show that the characteristics of the two type
of customers are opposite. They are the contrary, this could mean that ones are the
ones with churn = 1 (left the company) and the others the ones that stay. 
Also, looking at the data and the variables, the first factor can be the customers
that remain in the company, and the second factor the ones that leave the company.

This means that the first factors can contribute to the churn variable to be
negative, and the opposite for the second factor.
```

```{r factor analysis 2}
#check 1 and 2 factors again
par(mfrow=c(2,1))
barplot(x.f$loadings[,1], names=F, las=2, col="darkblue", ylim = c(-1, 1))
barplot(x.f$loadings[,2], las=2, col="darkblue", ylim = c(-1, 1))

# clean the environment.
rm(list = c("colsImportant")) 
```

#### Clustering

```{r Optimal Number of Clusters}
nFolds = 6
folds = sample(rep(1:nFolds, length.out = nrow(tele_num_scale_imp)))

for (i in 1:nFolds) {
    X = as.data.frame(tele_num_scale_imp)[which(folds == i), ]

    print(fviz_nbclust(X, kmeans, method = 'silhouette'))
}
```

Here, the graph indicates that mostly 3 clusters is the base clustering that we can make. 
And finally we will use a simple boostrapping to really know the best. However, as
boostrapping is really computationally expensive, we will do it for just one fold.

```{r one-fold bootstrapping}
X = as.data.frame(tele_num_scale_imp)[which(folds == 1), ]

fviz_nbclust(X, kmeans, method = 'gap_stat', k.max = 8)
```
```{r Kmeans}
X = as.data.frame(scale(tele_num_scale_imp))

#Considering three clusters
fit = kmeans(X, centers=3, nstart=100)
groups = fit$cluster

#Now, we will graph the number of ocurrencies for each group.
barplot(table(groups), col="#69b3a2")

#Here we see that there is a group with most of the customers, and other not so big. However, the second group is almost ineligible.  The hypothesis could be as the one we had before. One group can correspond to customers that left the company and other to the ones that remain. First, we will develop this cluster further, and then let's see if we can get the same hypothesis with other clustering methods.

centers = fit$centers

for (i in 1:3) {
    bar1=barplot(centers[i,], las=2, col="darkblue", ylim=c(-2,100),
                 main=paste("Cluster", i,
                            ": Group center in blue, global center in red"))
    print(points(bar1,y=apply(X, 2, quantile, 0.50),col="red",pch=19))
}

#Here, we can clearly see that the group with less values, is like a mix cluster.  The third cluster has much more higher values that other cluster, and this can mean that the customers from the third group are more radical and therefore have more probabilty to leave the company.

#ploting the cluster
fviz_cluster(fit, data = X, 
             geom = c("point"),
             ellipse.type = 'norm', 
             pointsize=1)+
    scale_fill_brewer(palette="Paired") +
    theme(panel.grid = element_blank(),
          panel.background = element_blank())

#Here we can see some minor differences and see that the most populated cluster (cluster 3) is at the left foremost part, followed by the first cluster and finally the second. This shows that number 2 are the most extreme customers and 1 the most common.    
```
```{r Mahalanobis distance K-Means}
S_x = cov(X)
iS = solve(S_x)
e = eigen(iS)
V = e$vectors
B = V %*% diag(sqrt(e$values)) %*% t(V)
Xtil = scale(X,scale = FALSE)
X_maha = as.data.frame(Xtil %*% B)

options(warn = -1)
fit.mahalanobis = kmeans(X_maha, centers=3, nstart=100)
groups = fit.mahalanobis$cluster
centers=fit.mahalanobis$centers
colnames(centers)=colnames(X)
#centers
barplot(table(groups), col="#69b3a2")

for (i in 1:3) {
    bar1=barplot(centers[i,], las=2, col="darkblue", ylim=c(-2,2), main=paste("Cluster", i,": Group center in blue, global center in red"))
    points(bar1,y=apply(X, 2, quantile, 0.50),col="red",pch=19)
}

#Not really the same. It is a little bit weird because the cluster that did not matter has a lot of outlier variables , whereas the most populated cluster (cluster 3) is almost 0. 

fviz_cluster(fit.mahalanobis, data = X, geom = c("point"),
             ellipse.type = 'norm', pointsize=1)+
    scale_fill_brewer(palette="Paired")+
    theme(panel.grid = element_blank(),
          panel.background = element_blank())

#The most popular clusters (cluster 2) are remain the same 
```

```{r Kernel K-Means}
fit.ker = kkmeans(as.matrix(X), centers=3, kernel="rbfdot") 
# Radial Basis kernel (Gaussian)
object.ker = list(data = X, cluster = fit.ker@.Data)

fviz_cluster(object.ker, geom = c("point"), ellipse=F,pointsize=1)
adjustedRandIndex(fit$cluster, fit.ker$cluster)
```
```{r Hierarchical Clustering}
d = dist(scale(X), method = "euclidean")
hc = hclust(d, method = "average")

hc$labels = names

plot(hc)

fviz_dend(x = hc, k = 3,color_labels_by_k = TRUE,cex = 0.8,
          type = "phylogenic",repel = TRUE)+
    theme(axis.text.x=element_blank(),axis.text.y=element_blank())

groups.hc = cutree(hc, k = 3)

fit.small = kmeans(X, centers=3, nstart=100)
adjustedRandIndex(fit.small$cluster, groups.hc)
```
```{r EM Clustering}
res.Mclust <- Mclust(scale(X))
summary(res.Mclust)

head(res.Mclust$classification)
fviz_mclust(object = res.Mclust, what = "BIC", pallete = "jco") +
    scale_x_discrete(limits = c(1:10))

fviz_mclust(object = res.Mclust, what = "classification", geom = "point",  
            pallete = "jco")
adjustedRandIndex(fit$clusters, res.Mclust$classification)
```


#### Prediction Models

* Get Dummies and Split training and testing dataset
```{r cateorical variables}
#subset
tele_cate = select_if(telecom1, is.character)
df1 = as.data.frame(cbind(tele_num_scale_imp, tele_cate, telecom1$churn))
df1 = df1 %>% rename(churn = `telecom1$churn`)
save(df1, file = "Categotical Selection.RData")

#get dummies
tele_cate1 = dummy_cols(tele_cate, select_columns = c("new_cell", "crclscod", "asl_flag", "area", "dualband", "refurb_new", "marital", "ethnic", "kid0_2", "kid3_5", "kid6_10", "kid11_15", "kid16_17", "creditcd" ))
tele_cate1 = tele_cate1[,-c(1:14)]

df = as.data.frame(cbind(tele_num_scale_imp, tele_cate1, telecom1$churn))
df = df %>% rename(churn = `telecom1$churn`)

save(df, file = "Prediction Data.RData")

#split
set.seed(157)
train <- sample(nrow(df), 0.7*nrow(df))
df.train <- df[train,]
df.test <- df[-train,]

X_train = df.train[,-147]
y_train = df.train[,147]
X_test = df.test[,-147]
y_test = df.test[,147]

#remove large data
rm(df)
```


###### supervised learning model selection
```{r}
df2 = as.data.frame(cbind(telecom_num_scale, tele_cate, telecom1$churn))
df2 = df2 %>% rename(churn = `telecom1$churn`)

#subset rows 
set.seed(157)
df3 = df2[sample(nrow(df2), 5000), ]
save(df3, file = "Model Selection.RData")
```



```{r backward}
add.mod = glm(churn~., family = binomial, data = df3)
back = step(add.mod, direction = "backward", trace = FALSE, scope = list(~ totmrc_Mean * vceovr_Mean * change_mou *
    change_rev * drop_vce_Mean * drop_dat_Mean * blck_vce_Mean * 
    blck_dat_Mean * threeway_Mean * mou_cvce_Mean * mou_rvce_Mean * 
    owylis_vce_Mean * mou_opkv_Mean * drop_blk_Mean * months * 
    uniqsubs * actvsubs * avgrev * hnd_price * phones * eqpdays * 
    asl_flag * area * refurb_new * ethnic))
summary(back)
```


```{r full_mod}
fit1 = glm(as.factor(churn) ~ totmrc_Mean + vceovr_Mean + change_mou + 
    change_rev + drop_vce_Mean + drop_dat_Mean + blck_vce_Mean + 
    blck_dat_Mean + threeway_Mean + mou_cvce_Mean + mou_rvce_Mean + 
    owylis_vce_Mean + mou_opkv_Mean + drop_blk_Mean + months + 
    uniqsubs + actvsubs + avgrev + hnd_price + phones + eqpdays + 
    as.factor(asl_flag) + as.factor(area) + as.factor(refurb_new) + as.factor(ethnic),family = binomial, data = df3)

coeffs <- coefficients(fit1)
coeffsord <- coeffs[order(coeffs, decreasing = TRUE)]


#par(mfrow=c(2,2))
plot(cooks.distance(fit1), type="h")
sort(cooks.distance(fit1), decreasing = TRUE)[1:5]

par(mfrow=c(2,2))
plot(fit1)
```


```{r}
cvfit = cv.glmnet(data.matrix(X_train), y_train, family="binomial", type.measure="mse")
A = predict(cvfit, newx=data.matrix(X_test), s="lambda.min", type="response")
RMSE1 = mean((y_test - A)^2)
RMSE1
```




```{r}
p = c("churn","totmrc_Mean","vceovr_Mean","change_mou","change_rev","drop_vce_Mean","drop_dat_Mean","blck_vce_Mean","drop_dat_Mean","threeway_Mean","mou_cvce_Mean","mou_rvce_Mean","owylis_vce_Mean","mou_opkv_Mean","drop_blk_Mean","months","uniqsubs","actvsubs","avgrev","hnd_price","phones","eqpdays","asl_flag","area","refurb_new","ethnic")
selected.vars = df3[,p]
ggcorrplot(cor(select_if(df3, is.numeric)), type = "lower")
```


```{r}
#split
set.seed(157)
train <- sample(nrow(selected.vars), 0.7*nrow(selected.vars))
df.train <- selected.vars[train,]
df.test <- selected.vars[-train,]

X_train = select(df.train,-c("churn"))
y_train = df.train[,c("churn")]
X_test = select(df.test,-c("churn"))
y_test = df.test[,c("churn")]
```

###### Logistic Regression

```{r ridge}
# 
set.seed(157)
ridge.cv = cv.glmnet(data.matrix(X_train), y_train, family = "binomial", alpha = 0)
ridge.lam = ridge.cv$lambda.min
plot(ridge.cv)
plot(ridge.cv$glmnet.fit, "lambda", label = TRUE)

ridge.pred = predict(ridge.cv, newx = data.matrix(X_test), s = "lambda.min")

 # the training error 
mean((ridge.pred - y_test)^2)

ridge.lam = ridge.cv$lambda.min
grid = 10^seq(10, -2, length = 100)
ridge_mod = glmnet(data.matrix(X_train), y_train, alpha=0, lambda = grid)
ridge_pred = predict(ridge_mod, s = ridge.lam, newx = data.matrix(X_test),type="response")
mean((ridge_pred - y_test)^2) 
ridge_coef = predict(ridge_mod, type = "coefficients", s = ridge.lam)
ridge_coef[ridge_coef!=0]
```



```{r lasso}
lasso.cv = cv.glmnet(data.matrix(X_train), y_train, family = "binomial", alpha=1)
plot(lasso.cv)
plot(lasso.cv$glmnet.fit, "lambda", label = TRUE)
lasso.lam = lasso.cv$lambda.min 
grid = 10^seq(10, -2, length = 100)
lasso_mod = glmnet(X_train, y_train, alpha = 1, lambda = grid)
plot(lasso_mod, label = TRUE)
lasso_pred = predict(lasso_mod, s = lasso.lam, newx = data.matrix(X_test),type="response")
mean((lasso_pred - y_test)^2)
lasso_coef = predict(lasso_mod, type = "coefficients", s = lasso.lam)
lasso_coef[lasso_coef!=0]
```



```{r}
enet.fit = cv.glmnet(data.matrix(X_train), y_train,family = "binomial", nfolds = 10, alpha = 0.5)
plot(enet.fit)
plot(enet.fit$glmnet.fit, "lambda", label = TRUE)
enet.lam = enet.fit $lambda.min 
grid = 10^seq(10, -2, length = 100)
lasso_mod = glmnet(X_train, y_train, alpha = 1, lambda = grid)
plot(lasso_mod, label = TRUE)
lasso_pred = predict(lasso_mod, s = lasso.lam, newx = data.matrix(X_test),type="response")
mean((lasso_pred - y_test)^2)
lasso_coef = predict(lasso_mod, type = "coefficients", s = lasso.lam)
lasso_coef[lasso_coef!=0]
```




```{r class}
#Classification
ypred = 1*(predict(cvfit, newx= data.matrix(X_test),
                   s="lambda.min", type="response")>0.5)
cmat2 = table(ypred, ytrue=y_test)
cmat2
sens = cmat2["1","1"]/(cmat2["0","1"]+cmat2["1","1"])
spec = cmat2["0","0"]/(cmat2["0","0"]+cmat2["1","0"])
data.frame(sens, spec)

```


```{r auc}

cvfit1 = cv.glmnet(data.matrix(X_train), y_train, family = "binomial", alpha=0.5, nlambda = 24, type.measure="auc", keep=TRUE)
cvfit1$index
plot(cvfit1)
rocs = roc.glmnet(cvfit1$fit.preval, newy = y_train)
best = cvfit1$index["min",]
par(pty="s", mar=c(4,4,0.1,0.1)); plot(rocs[[best]], type = "l")
invisible(sapply(rocs, lines, col="orange"))
lines(rocs[[best]], lwd = 2, col = "blue"); lines(c(0,1),c(0,1), lty=2)

confusion.glmnet(cvfit1, newx = data.matrix(X_test), newy = y_test)

bestbeta = coef(cvfit1, s = "lambda.min")
  
  # number of nonzero parameters
  sum(as.numeric(bestbeta)!=0)
   # the list of nonzero parameters
  selected = data.frame("gene names" = rownames(bestbeta), 
                        "beta" = as.numeric(bestbeta))[as.numeric(bestbeta)!=0, ]
  
  # sort
  coef = selected[order(selected$beta, decreasing = TRUE), ]
barplot(coef$beta, names = coef$gene.names, las=2, main = "Coefficients")
```



```{r}
cvfit0 = cv.glmnet(data.matrix(X_train), y_train, family="binomial")
pred0 = predict(cvfit0, newx=data.matrix(X_test), s="lambda.min", type="response")
```

```{r}
  library(ROCR)
pred1 = predict(lasso.cv, newx= data.matrix(X_test),
                   s="lambda.min", type="response")
pred2 = predict(ridge.cv, newx= data.matrix(X_test),
                   s="lambda.min", type="response")
roc1 <- prediction(pred1, df.test$churn)
roc2 <- prediction(pred2, df.test$churn)
roc0 <- prediction(pred0, df.test$churn)
  
  # calculates the ROC curve
  perf1 <- performance(roc1,"tpr","fpr")
  perf2 <- performance(roc2,"tpr","fpr")
  perf0 <- performance(roc0,"tpr","fpr")
    plot(perf1, col="red")
    plot(perf2, col = "blue", add = TRUE)
    plot(perf0, col = "green", add = TRUE)
    legend("bottomright",legend=c("Lasso", "Ridge", "GLM"), col=c("red", "blue", "green"),lty = 1)
   performance(roc1, measure = "auc")@y.values[[1]]
   performance(roc2, measure = "auc")@y.values[[1]]
   performance(roc0, measure = "auc")@y.values[[1]]
```






###### Decision Tree
```{r decision tree}
df.fit <- ctree(as.factor(churn) ~ ., data = df.train)
pre5 <- predict(df.fit, X_test)
mean(pre5 == y_test)
```

###### Random Forest
```{r rf}
tuneGrid = expand.grid(.mtry = c(1:20))
trControl = trainControl(method = "cv", number = 10)

rf_mtry = train(as.factor(churn)~., data=df, method = "rf", metric = "Accuracy", tuneGrid = tuneGrid, trControl = trControl,
             num.trees = 100,
             respect.unordered.factors = "partition")
best.mtry = rf_mtry$bestTurn$mtry

store.maxnode = list()
TurneGrid = expand.grid(.mtry = best.mtry)
for (maxnodes in 2:10){
  set.seed(1)
  rf_maxnode = train(as.factor(churn)~., data=tele_cate, method = "rf", metric = "Accuracy", tuneGrid = TuneGrid, trControl = trControl,
             ntrees = 300,
             maxnodes = 10 )
  current_iteration <- toString(nodeize)
  store.maxnode[[current_iteration]] <- rf_nodeszie
}
results.nodesize <- resample(store.maxnode)
summary(results.nodesize)

store.tree<-list()
for (ntree  in seq(100:1000, 150)){
  set.seed(1)
  rf_maxtree = train(as.factor(churn)~., data=df1, method = "rf", metric = "Accuracy", tuneGrid = TuneGrid, trControl = trControl,
             maxnodes = 10,
             ntree = ntree )
  key <- toString(ntree)
  store.tree[[key]]<-rf_maxtree
}
result_tree <- resamples(store.tree)
summary(result_tree)


rf.fit <- train(as.factor(churn)~., data=df1, method = "rf", metric = "Accuracy", tuneGrid = TuneGrid, trControl = trControl,
             ntrees = 300, nodesize = 2, maxnodes = 5 )
varImp(rf.fit)
```

###### SVM
```{r svm}
  cost.grid = expand.grid(cost = seq(0.01, 2, length = 20))
  train_control = trainControl(method="repeatedcv", number=10, repeats=3)
  
  svm2 <- train(y_train ~ X_train, data = df.train, method = "svmLinear2", 
                trControl = train_control,  
                tuneGrid = cost.grid)
```

###### KNN
```{r knn}
#control = trainControl(method = "cv", number = 10)
#set.seed(157)
#knn.cvfit <- train(X_train, as.factor(y_train), method = "knn",data = df.train,tuneGrid = data.frame(k = seq(1,10,1)),trControl = control)


#knn.fit <- knn(df.train, df.test, y_train, k = sqrt(length(train))

#pred_knn <- knn(churn ~ .,df.train,df.test,k=15)
```





