---
title: "Telecom Customer Churn Prediction"
author: "Xiaoying Yang, Bo Yang, Yin Tip Ho"
date: "4/28/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem Statement
需要陈述


## Target

Predict which characteristics of customers are most likely to lose and put forward suggestions for retaining users to the maximum extent according to the properties of losing customers.
初稿

## Data Description

This data set consists of 100 variables and approximately 100 thousand records. 
This data set contains different variables explaining the attributes of telecom industry and various factors considered important while dealing with customers of telecom industry. 
The target variable here is churn which explains whether the customer will churn or not.

#### Customer Usage Behavior  #1-48 需要添加col number，麻烦Bo Yang啦，把你的copy过来 

* Price #1, 3, 6, 11
* Calling #
* Flow
* Time 不太明白这个跟calling、flow的关系，只是说用的比较多吗

#### Customer Atributes #50-99

* Interaction with Telecom Operators
* Family
* Social Relations
* Financial Assets
* Facilities
* Others

#### Variable Description
1 rev_Mean: Mean monthly revenue (charge amount)
2 mou_Mean: Mean number of monthly minutes of use
3 totmrc_Mean: Mean total monthly recurring charge
4 da_Mean: Mean number of directory assisted calls
5 ovrmou_Mean: Mean overage minutes of use
6 ovrrev_Mean: Mean overage revenue
7 vceovr_Mean: Mean revenue of voice overage
8 datovr_Mean: Mean revenue of data overage
9 roam_Mean: Mean number of roaming calls
10 change_mou: Percentage change in monthly minutes of use vs previous three month average
11 change_rev: Percentage change in monthly revenue vs previous three month average
12 drop_vce_Mean: Mean number of dropped (failed) voice calls
13 drop_dat_Mean: Mean number of dropped (failed) data calls
14 blck_vce_Mean: Mean number of blocked (failed) voice calls
15 blck_dat_Mean: Mean number of blocked (failed) data calls
16 unan_vce_Mean: Mean number of unanswered voice calls
17 unan_dat_Mean: Mean number of unanswered data calls
18 plcd_vce_Mean: Mean number of attempted voice calls placed
19 plcd_dat_Mean: Mean number of attempted data calls placed
20 recv_vce_Mean: Mean number of received voice calls
21 recv_sms_Mean: N
22 comp_vce_Mean: Mean number of completed voice calls
23 comp_dat_Mean: Mean number of completed data calls
24 custcare_Mean: Mean number of customer care calls
25 ccrndmou_Mean: Mean rounded minutes of use of customer care calls
26 cc_mou_Mean: Mean unrounded minutes of use of customer care (see CUSTCARE_MEAN) calls
27 inonemin_Mean: Mean number of inbound calls less than one minute
28 threeway_Mean: Mean number of three way calls
29 mou_cvce_Mean: Mean unrounded minutes of use of completed voice calls
30 mou_cdat_Mean: Mean unrounded minutes of use of completed data calls
31 mou_rvce_Mean: Mean unrounded minutes of use of received voice calls
32 owylis_vce_Mean: Mean number of outbound wireless to wireless voice calls
33 mouowylisv_Mean: Mean unrounded minutes of use of outbound wireless to wireless voice calls
34 iwylis_vce_Mean: N
35 mouiwylisv_Mean: Mean unrounded minutes of use of inbound wireless to wireless voice calls
36 peak_vce_Mean: Mean number of inbound and outbound peak voice calls
37 peak_dat_Mean: Mean number of peak data calls
38 mou_peav_Mean: Mean unrounded minutes of use of peak voice calls
39 mou_pead_Mean: Mean unrounded minutes of use of peak data calls
40 opk_vce_Mean: Mean number of off-peak voice calls
41 opk_dat_Mean: Mean number of off-peak data calls
42 mou_opkv_Mean: Mean unrounded minutes of use of off-peak voice calls
43 mou_opkd_Mean: Mean unrounded minutes of use of off-peak data calls
44 drop_blk_Mean: Mean number of dropped or blocked calls
45 attempt_Mean: Mean number of attempted calls
46 complete_Mean: Mean number of completed calls
47 callfwdv_Mean: Mean number of call forwarding calls
48 callwait_Mean: Mean number of call waiting calls
49 churn: Instance of churn between 31-60 days after observation date
50 months: Total number of months in service
51 uniqsubs: Number of unique subscribers in the household
52 actvsubs: Number of active subscribers in household
53 new_cell: New cell phone user
54 crclscod: Credit class code
55 asl_flag: Account spending limit
56 totcalls: Total number of calls over the life of the customer
57 totmou: Total minutes of use over the life of the cus
58 totrev: Total revenue
59 adjrev: Billing adjusted total revenue over the life of the customer
60 adjmou: Billing adjusted total minutes of use over the life of the customer
61 adjqty: Billing adjusted total number of calls over the life of the customer
62 avgrev: Average monthly revenue over the life of the customer
63 avgmou: Average monthly minutes of use over the life of the customer
64 avgqty: Average monthly number of calls over the life of the customer
65 avg3mou: Average monthly minutes of use over the previous three months
66 avg3qty: Average monthly number of calls over the previous three months
67 avg3rev: Average monthly revenue over the previous three months
68 avg6mou: Average monthly minutes of use over the previous six months
69 avg6qty: Average monthly number of calls over the previous six months
70 avg6rev: Average monthly revenue over the previous six months
71 prizm_social_one: Social group letter only
72 area: Geogrpahic area
73 dualband: Dualband
74 refurb_new: Handset: refurbished or new
75 hnd_price: Current handset price
76 phones: Number of handsets issued
77 models: Number of models issued
78 hnd_webcap: Handset web capability
79 truck: Truck indicator
80 rv: RV indicator
81 ownrent: Home owner/renter status
82 lor: Length of residence
83 dwlltype: Dwelling Unit type
84 marital: Marital Status
85 adults: Number of adults in household
86 infobase: InfoBase match
87 income: Estimated income
88 numbcars: Known number of vehicles
89 HHstatin: Premier household status indicator
90 dwllsize: Dwelling size
91 forgntvl: Foreign travel dummy variable
92 ethnic: Ethnicity roll-up code
93 kid0_2: Child 0 - 2 years of age in household
94 kid3_5: Child 3 - 5 years of age in household
95 kid6_10: Child 6 - 10 years of age in household
96 kid11_15: Child 11 - 15 years of age in household
97 kid16_17: Child 16 - 17 years of age in household
98 creditcd: Credit card indicator
99 eqpdays: Number of days (age) of current equipment
100 Customer_ID: N

## Project Guide 到时候做完再改动

* Data Wrangling
    + Missing Values 
* Feature Engineering
    + get dummies
    + check correlation
    + scaling 
* Exploratory Data Analysis (EDA) 
    + How much does customer spend on telecom monthly?
    + 类似这种？看我们需不需要，就是比较麻烦，我只写了一个
* Factor Analysis and Clustering
* Regression Prediction
    + 分出来training(60%), cross-validation(20%),testing(20%)

## References
https://www.kaggle.com/datasets/abhinav89/telecom-customer

## CODE
#### Data Wrangling

* Import Data and load library
建议把所有要用的library写在这啦，避免重复loading
```{r Import Data and load library}
    library(tidyverse)
    library(zoo)
    library(gtools)
    library(naniar)
    library(mice)
    library(ggcorrplot)
    library(rlang)
    library(factoextra)
    raw_data <- read_csv("Telecom_customer churn.csv")
```

* Missing Values

```{r Check missing values by column}
#check missing values by columns
raw_data %>% miss_var_summary()

#Remove the columns with more than 10% missing values 
telecom <- raw_data %>%
    select(-c(numbcars, HHstatin, dwllsize, ownrent, dwlltype, lor,income, 
              adults, infobase, hnd_webcap)) %>%
    select(-prizm_social_one)  #remove unrelated col with high missing rate

telecom1 <- telecom
var_miss <- which(colMeans(is.na(telecom1))!= 0)
var_miss
# 33 variables still have missing value.

# Numeric type var
nr_mice <- select_if(telecom1, negate(is.numeric))
r_mice <- select_if(telecom1, is.numeric)
na_mice <- r_mice[, c(69, 70, 74)]
r_mice <- r_mice[, -c(69, 70, 74)]

# Imputation by rf
impute <- mice(r_mice, method = "rf", ntree = 50, m = 1, maxit = 1)
telecom_complete <- complete(impute)
any(is.na(telecom_complete))
# Add non-numeric type var back to the data set
telecom1 <- cbind(telecom_complete, na_mice, nr_mice)
sum(is.na(telecom1))
var_miss1 <- which(colMeans(is.na(telecom1))!= 0)
var_miss1
# Row missing value
row_miss <- which(rowMeans(is.na(telecom1)) != 0)
length(row_miss)

telecom1 <- telecom1[-row_miss, ]

save(telecom1, file = "telecom_Comsumer_Info.RData")
```


#### Feature Engineering

Transform some numeric variables into factors because they are only 0 or 1.
Create a separate data set without the churn variable (variable to predict) that will be the one we work on.
Enumerate the rows of the data set with the Customers ID so we can identify each.
Remove unnecessary variables with a correlation matrix, and remove some that are also not important.

参考 https://www.kaggle.com/code/clustercode12/telecom-churn-analysis-with-r/notebook

```{r}
# Function to transform variables
REMOVE = "remove"
TO_FACTOR = "tofactor"

editCol <- function(colNames, df, todo) {
  for(col in colNames) {
    index <- which(names(df) == col)
    if(!is_empty(index)) {
      if(todo == REMOVE) {
        df <- df[, -index]
      } else if(todo == TO_FACTOR) {
        df[, index]  <- as.factor(df[, index])
      } else {errorCondition("Not performing well")}
    }
  }
  return(df)
}

# Perform the function
telecom1 <- editCol(c("forgntv1", "truck", "rv"), telecom1, TO_FACTOR)
telecom1 <- droplevels.data.frame(telecom1)
row.names(telecom1) <- telecom1$Customer_ID
telecom_customer <- telecom1
telecom1 <- editCol(c("churn", "Customer_ID"), telecom1, REMOVE)

rm(list = setdiff(ls(), c("telecom1", "telecom_customer")))

# Correlation matrix
r_mice <- select_if(telecom1, is.numeric)
Corr <- cor(r_mice)
Corr[upper.tri(Corr)] = 0
ggcorrplot(corr = Corr, method = "square", lab = FALSE)
# correlation heat-map
col<- colorRampPalette(c("blue", "white", "red"))(20)
heatmap(x = Corr, col = col, symm = TRUE)

  # Need to eliminate strong correlated variables
diag(Corr) = 0
 
telecom_num_no_corr <-  r_mice[, !apply(Corr, 2, function(x) any(abs(x) > 0.9, na.rm = TRUE))]
# How many variables are eliminated
dim(r_mice)[2] - dim(telecom_num_no_corr)[2]
```


```{r}
 #hist
    par(mfrow = c(3,4))
    for (i in 1:ncol(telecom_num_no_corr)){
        hist(telecom_num_no_corr[,i],
             breaks = 30,
             main = "",ylab = "",
             xlab = names(telecom_num_no_corr)[i],
             cex.axis=0.5,
             cex.lab = 0.6)
    }
    
    #scaling and his again
    telecom_num_scale = scale(telecom_num_no_corr)
     par(mfrow = c(3,4))
    for (i in 1:ncol(telecom_num_scale)){
        hist(telecom_num_scale[,i],
             breaks = 30,
             main = "",ylab = "",
             xlab = names(telecom_num_no_corr)[i],
             cex.axis=0.5,
             cex.lab = 0.6)
    }

    
```


#### PCA
Principle Components Analysis

```{r}
pca_tele <- prcomp(telecom_num_scale)
# pca_tele #发现太长了就用summary
summary(pca_tele)
var_expalained <- pca_tele$sdev^2/sum(pca_tele$sdev^2)

# Scree plot
fviz_screeplot(pca_tele, addlabels = TRUE) # Scree plot
qplot(c(1:49), var_expalained) + geom_line() + xlab("Principal Component") + ylab("Variance Explained") + ggtitle("Scree Plot") + ylim(0, 1)
print(var_expalained)

# Visualize contributions of pca in different dimensions
fviz_contrib(pca_tele,choice = "var", axes = 1)
fviz_contrib(pca_tele,choice = "var", axes = 2)
fviz_contrib(pca_tele,choice = "var", axes = 3)

# MCA for individual
fviz_contrib(pca_tele, choice = "ind", axes = 2, top = 100)# Difference between customers

# PCA RADOR PLOT
fviz_pca_var(pca_tele, col.var = "contrib")

# PCA biplot
fviz_pca_biplot(pca_tele, repel = TRUE)

# Customers on 1st and 2nd components
fviz_pca_ind(pca_tele,
             label = "none", # hide individual labels
             habillage = telecom_complete$churn, # color by groups
             palette = c("#00AFBB", "#E7B800"))
#ggg
#testing function:  pls no error
```

```




#### EDA
e.g How much does customer spend on telecom monthly?
```{r}
    range(telecom$rev_Mean, na.rm = T)

    ggplot(data = telecom, aes(x = rev_Mean, fill = churn))+
        geom_histogram() +
        theme(panel.background = element_blank(),
              panel.grid = element_blank())
    
    #因为没有处理异常值的原因所以看不出来啥
```


